Beliefs about the development of mental life

### 2022-08-01 supplement/supplement-main.Rmd
begin updating analyses... should have committed earlier...

To assess which developmental mechanisms were considered to be the most or least important in the development of each of the individual mental capacities included in this study (*bodily sensation*, *negative affect*, *social connection*, and *cognition and control*), we conducted a multilevel linear regression regressing responses to this question onto type of developmental mechanism (extrinsic vs. intrinsic), domain, and an interaction between them, including the maximal random effects structure that allowed the model to converge. Using the "lme4" package for R [@bates.etal2015], we specified this model as follows: _lmer(response ~ mechanism type * domain + (1 + mechanism type + domain | participant) + (1 | developmental mechanism) + (1 | capacity)_. We also conducted separate, analogous regression analyses for each domain separately. In these analyses, mechanism type and domain were effect-coded for comparisons to the grand mean collapsing across mechanism types and domains. (Note that these analyses omitted the mechanism "the child's brain changes [...]", because it was the only mechanism that was difficult to classify as either intrinsic or extrinsic via EFA and clustering analyses; see previous section.)

The full results of these models are presented in Supplementary Tables \@ref(tab:tabs3lmerall) (all domains), \@ref(tab:tabs3lmerbod) (*bodily sensation*), \@ref(tab:tabs3lmerneg) (*negative affect*), \@ref(tab:tabs3lmersoc) (*social connection*), and \@ref(tab:tabs3lmercog) (*cognition and control*); see also Figure 3 (main text).

```{r s3 mech ratings datasets b}
d3_mech_ratings <- d3_dev_factor_rating %>%
  mutate(factor = recode_factor(domain,
                                "BOD"= "Bodily sensation",
                                "NEG" = "Negative affect",
                                "POS" = "Social connection",
                                "COG" = "Cognition and control")) %>%
  select(-domain) %>%
  mutate(dev_factor_cluster = case_when(
    dev_factor %in% c("senses_improve", "body_grows", 
                      "womb_experiences", "preprogrammed") ~ "intrinsic",
    dev_factor %in% c("interacts_people", "observes_people", "observes_objects", 
                      "people_teach", "experiments") ~ "extrinsic",
    dev_factor == "brain_changes" ~ NA_character_,
    TRUE ~ NA_character_
  )) %>%
  mutate(dev_factor_cluster = factor(dev_factor_cluster,
                                     levels = c("intrinsic", "extrinsic")))

@@

contrasts(d3_mech_ratings$dev_factor_cluster) <- cbind(ext_gm = c(-1, 1))
```

```{r s3 mech ratings summary stats}
# overall
d3_mech_ratings_sum_a <- d3_mech_ratings %>%
  filter(!is.na(dev_factor_cluster)) %>%
  # participant-level mean of means for each cluster
  group_by(ResponseId, dev_factor_cluster) %>%
  summarise(score_a = mean(response, na.rm = T)) %>%
  ungroup() %>%
  # group-level mean of means for each cluster 
  group_by(dev_factor_cluster) %>%
  summarise(median = median(score_a, na.rm = T),
            mean = mean(score_a, na.rm = T),
            sd = sd(score_a, na.rm = T)) %>%
  ungroup() %>%
  arrange(dev_factor_cluster)

@@

# by domain
d3_mech_ratings_sum_b <- d3_mech_ratings %>%
  filter(!is.na(dev_factor_cluster)) %>%
  # participant-level mean for each mechanism, for each domain
  group_by(ResponseId, dev_factor_cluster, dev_factor, factor) %>%
  summarise(score_a = mean(response, na.rm = T)) %>%
  ungroup() %>%
  # participant-level mean of means for each cluster, for each domain
  group_by(ResponseId, dev_factor_cluster, factor) %>%
  summarise(score_b = mean(score_a, na.rm = T)) %>%
  ungroup() %>%
  # group-level mean of means of means for each domain 
  group_by(dev_factor_cluster, factor) %>%
  summarise(median = median(score_b, na.rm = T),
            mean = mean(score_b, na.rm = T),
            sd = sd(score_b, na.rm = T)) %>%
  ungroup() %>%
  arrange(factor, dev_factor_cluster)

d3_mech_ratings_sum_b %>%
  mutate_if(is.numeric, funs(round_x(., 2)))

# mean DIFFERENCES by domain
d3_mech_ratings_sum_c <- d3_mech_ratings %>%
  filter(!is.na(dev_factor_cluster)) %>%
  # participant-level mean for each cluster, for each capacity
  group_by(ResponseId, dev_factor_cluster, factor, capacity) %>%
  summarise(score_a = mean(response, na.rm = T)) %>%
  ungroup() %>%
  # participant-level cluster differences for each capacity
  spread(dev_factor_cluster, score_a) %>%
  mutate(diff_a = extrinsic - intrinsic) %>%
  select(-extrinsic, -intrinsic) %>%
  # participant-level mean differences, for each domain
  group_by(ResponseId, factor) %>%
  summarise(diff_b = mean(diff_a, na.rm = T)) %>%
  ungroup() %>%
  # group-level mean of means of mean differences, for each domain 
  group_by(factor) %>%
  summarise(median = median(diff_b, na.rm = T),
            mean = mean(diff_b, na.rm = T),
            sd = sd(diff_b, na.rm = T)) %>%
  ungroup() %>%
  arrange(factor)

d3_mech_ratings_sum_c %>%
  mutate_if(is.numeric, funs(round_x(., 2)))
```

In brief, this analysis suggested that, collapsing across domains, intrinsic and extrinsic mechanisms were rated as equally important, but that the difference between intrinsic and extrinsic mechanisms varied across domains (see interaction terms).

```{r s3 mech ratings lmer}
s3_lmer <- lmer(response ~ dev_factor_cluster * factor + 
                  (1 + dev_factor_cluster + factor | ResponseId) + 
                  (1 | dev_factor) +
                  (1 | capacity),
                control = lmerControl(optimizer = "bobyqa"),
                data = d3_mech_ratings)

@@

```{r tabs3lmerall, include = T, message = F, warning = F}
model_parameters(s3_lmer, standardize = "refit") %>%
  filter(Effects == "fixed") %>%
  select(Parameter, Coefficient, SE, CI_low, CI_high, t, df_error, p) %>%
  mutate(Parameter = case_when(
    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
    TRUE ~ Parameter)) %>%
  mutate(Parameter = gsub("dev_factor_clusterext_gm", "Mechanism type (Extrinsic vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
  select(-starts_with("CI")) %>%
  select(Parameter, Coefficient, `95% CI`, everything()) %>%
  rename(df = df_error) %>%
  kable("latex", booktabs = T, longtable = T,
        caption = "Study 3, multilevel linear model results (all domains): Fixed effects.",
        digits = 2, align = c("lrrrrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

##### Bodily sensation

For capacities in the domain of _bodily sensation_, this analysis suggested that participants rated intrinsic mechanisms as more important drivers of development than extrinsic mechanisms; see also Figure 3, panels A-B (main text).

```{r s3 mech ratings lmer bod}
s3_lmer_bod <- lmer(response ~ dev_factor_cluster + 
                      (1 + dev_factor_cluster | ResponseId) + 
                      (1 | dev_factor) + 
                      (1 | capacity),
                control = lmerControl(optimizer = "bobyqa"),
                data = d3_mech_ratings %>% 
                  filter(factor == "Bodily sensation"))

summary(s3_lmer_bod)
# model_parameters(s3_lmer)
```

```{r tabs3lmerbod, include = T, message = F, warning = F}
model_parameters(s3_lmer_bod, standardize = "refit") %>%
  filter(Effects == "fixed") %>%
  select(Parameter, Coefficient, SE, CI_low, CI_high, t, df_error, p) %>%
  mutate(Parameter = case_when(
    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
    TRUE ~ Parameter)) %>%
  mutate(Parameter = gsub("dev_factor_clusterext_gm", "Mechanism type (Extrinsic vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
  select(-starts_with("CI")) %>%
  select(Parameter, Coefficient, `95% CI`, everything()) %>%
  rename(df = df_error) %>%
  kable("latex", booktabs = T, longtable = T,
        caption = "Study 3, multilevel linear model results (bodily sensation): Fixed effects.",
        digits = 2, align = c("lrrrrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

For capacities in the domain of _negative affect_, this analysis suggested that participants rated intrinsic and extrinsic mechanisms as equally important drivers of development; see also Figure 3, panels A-B (main text).

```{r s3 mech ratings lmer neg}
s3_lmer_neg <- lmer(response ~ dev_factor_cluster + 
                      (1 + dev_factor_cluster | ResponseId) + 
                      (1 | dev_factor) + 
                      (1 | capacity),
                control = lmerControl(optimizer = "bobyqa"),
                data = d3_mech_ratings %>% 
                  filter(factor == "Negative affect"))

summary(s3_lmer_neg)
# model_parameters(s3_lmer)
```

```{r tabs3lmerneg, include = T, message = F, warning = F}
model_parameters(s3_lmer_neg, standardize = "refit") %>%
  filter(Effects == "fixed") %>%
  select(Parameter, Coefficient, SE, CI_low, CI_high, t, df_error, p) %>%
  mutate(Parameter = case_when(
    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
    TRUE ~ Parameter)) %>%
  mutate(Parameter = gsub("dev_factor_clusterext_gm", "Mechanism type (Extrinsic vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
  select(-starts_with("CI")) %>%
  select(Parameter, Coefficient, `95% CI`, everything()) %>%
  rename(df = df_error) %>%
  kable("latex", booktabs = T, longtable = T,
        caption = "Study 3, multilevel linear model results (negative affect): Fixed effects.",
        digits = 2, align = c("lrrrrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

For capacities in the domain of _social connection_, this analysis suggested that participants rated extrinsic mechanisms as more important drivers of development than intrinsic mechanisms; see also Figure 3, panels A-B (main text).

```{r s3 mech ratings lmer soc}
s3_lmer_soc <- lmer(response ~ dev_factor_cluster + 
                      (1 + dev_factor_cluster | ResponseId) + 
                      (1 | dev_factor) + 
                      (1 | capacity),
                control = lmerControl(optimizer = "bobyqa"),
                data = d3_mech_ratings %>% 
                  filter(factor == "Social connection"))

summary(s3_lmer_soc)
# model_parameters(s3_lmer)
```

```{r tabs3lmersoc, include = T, message = F, warning = F}
model_parameters(s3_lmer_soc, standardize = "refit") %>%
  filter(Effects == "fixed") %>%
  select(Parameter, Coefficient, SE, CI_low, CI_high, t, df_error, p) %>%
  mutate(Parameter = case_when(
    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
    TRUE ~ Parameter)) %>%
  mutate(Parameter = gsub("dev_factor_clusterext_gm", "Mechanism type (Extrinsic vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
  select(-starts_with("CI")) %>%
  select(Parameter, Coefficient, `95% CI`, everything()) %>%
  rename(df = df_error) %>%
  kable("latex", booktabs = T, longtable = T,
        caption = "Study 3, multilevel linear model results (social connection): Fixed effects.",
        digits = 2, align = c("lrrrrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

For capacities in the domain of _cognition and control_, this analysis suggested that participants rated extrinsic mechanisms as much more important drivers of development than intrinsic mechanisms; see also Figure 3, panels A-B (main text).

```{r s3 mech ratings lmer cog}
s3_lmer_cog <- lmer(response ~ dev_factor_cluster + 
                      (1 + dev_factor_cluster | ResponseId) + 
                      (1 | dev_factor) + 
                      (1 | capacity),
                control = lmerControl(optimizer = "bobyqa"),
                data = d3_mech_ratings %>% 
                  filter(factor == "Cognition and control"))

summary(s3_lmer_cog)
# model_parameters(s3_lmer)
```

```{r tabs3lmercog, include = T, message = F, warning = F}
model_parameters(s3_lmer_cog, standardize = "refit") %>%
  filter(Effects == "fixed") %>%
  select(Parameter, Coefficient, SE, CI_low, CI_high, t, df_error, p) %>%
  mutate(Parameter = case_when(
    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
    TRUE ~ Parameter)) %>%
  mutate(Parameter = gsub("dev_factor_clusterext_gm", "Mechanism type (Extrinsic vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
  select(-starts_with("CI")) %>%
  select(Parameter, Coefficient, `95% CI`, everything()) %>%
  rename(df = df_error) %>%
  kable("latex", booktabs = T, longtable = T,
        caption = "Study 3, multilevel linear model results (cognition and control): Fixed effects.",
        digits = 2, align = c("lrrrrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

```{r fig03a, fig.width = 4.5, fig.asp = 1.5}
fig03a <- d3_mech_ratings %>%
  mutate(dev_factor_cluster = case_when(
    is.na(dev_factor_cluster) ~ "Other",
    dev_factor_cluster == "intrinsic" ~ "INTRINSIC mechanisms",
    dev_factor_cluster == "extrinsic" ~ "EXTRINSIC mechanisms"),
    dev_factor_cluster = factor(dev_factor_cluster,
                                levels = c("INTRINSIC mechanisms", 
                                           "EXTRINSIC mechanisms",
                                           "Other")),
    dev_factor_text = recode_factor(
      dev_factor,
      "preprogrammed" = "biologically ‘preprogrammed'",
      "womb_experiences" = "experiences in the womb",
      "body_grows" = "body grows and matures",
      "brain_changes" = "brain changes",
      "senses_improve" = "senses improve",
      "observes_objects" = "observes objects and physical world",
      "experiments" = "actively experiments",
      "observes_people" = "observes people",
      "interacts_people" = "interacts with people",
      "people_teach" = "people explicitly teach"),
    capacity = str_wrap(gsub("_", " ", capacity), 14)) %>%
  ggplot(aes(x = reorder(str_wrap(dev_factor_text, 20), 
                         as.numeric(dev_factor)), 
             y = response, color = factor)) +
  facet_grid(rows = vars(reorder(capacity, as.numeric(factor))),
             cols = vars(dev_factor_cluster),
             scales = "free", space = "free") +
  geom_hline(yintercept = 3, lty = 2, color = "darkred") +
  geom_jitter(alpha = 0.6, size = 0.02) +
  geom_pointrange(data = . %>%
                    group_by(factor, capacity, 
                             dev_factor_cluster, 
                             dev_factor, dev_factor_text) %>%
                    multi_boot_standard(col = "response") %>%
                    ungroup(),
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
                  color = "black", fatten = 2) +
  scale_color_viridis_d(end = 0.9, option = "viridis") +
  scale_y_continuous(breaks = seq(0, 6, 3), minor_breaks = seq(0, 6, 1)) +
  theme_minimal() +
  theme(panel.background = element_rect(fill = NA), 
        strip.text = element_text(vjust = 0),
        legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
        # plot.margin = unit(c(0.5, 0.5, 0.5, 1.1), "cm")) +
  labs(x = "Developmental mechanism",
       y = "Response (0 = not at all important, 6 = extremely important)",
       color = "Domain") +
  guides(color = guide_legend(override.aes = list(alpha = 1, size = 2)))
```

>>>>

To supplement our visual assessment of which developmental mechanisms were considered to be the most or least important in the development of each of the individual mental capacities included in this study (*bodily sensation*, *negative affect*, *social connection*, and *cognition and control*), we conducted a series of multilevel linear regression models, regressing responses to this question onto domain, including the maximal random effects structure that allowed the model to converge. Using the "lme4" package for R [@bates.etal2015], we specified these models as follows: _lmer(response ~ domain + (1 | participant) + (1 | capacity)_. In these analyses, domain and developmental mechanism were both effect-coded for comparisons to the grand mean collapsing across domains and mechanisms.

The full results of these models are presented in Supplementary Tables xxxxxxx; see also Figure 3 (main text).

```{r s3 mech ratings datasets b}
d3_mech_ratings <- d3_dev_factor_rating %>%
  mutate(factor = recode_factor(domain,
                                "BOD"= "Bodily sensation",
                                "NEG" = "Negative affect",
                                "POS" = "Social connection",
                                "COG" = "Cognition and control")) %>%
  select(-domain)

@@

contrasts(d3_mech_ratings$dev_factor) <- cbind(
  womb_gm = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0),
  body_gm = c(-1, 0, 1, 0, 0, 0, 0, 0, 0, 0),
  brai_gm = c(-1, 0, 0, 1, 0, 0, 0, 0, 0, 0),
  sens_gm = c(-1, 0, 0, 0, 1, 0, 0, 0, 0, 0),
  obso_gm = c(-1, 0, 0, 0, 0, 1, 0, 0, 0, 0),
  expt_gm = c(-1, 0, 0, 0, 0, 0, 1, 0, 0, 0),
  obsp_gm = c(-1, 0, 0, 0, 0, 0, 0, 1, 0, 0),
  intp_gm = c(-1, 0, 0, 0, 0, 0, 0, 0, 1, 0),
  teac_gm = c(-1, 0, 0, 0, 0, 0, 0, 0, 0, 1))
```

```{r s3 mech ratings summary stats}
# overall
d3_mech_ratings_sum_a <- d3_mech_ratings %>%
  # participant-level mean of means for each mechanism
  group_by(ResponseId, dev_factor) %>%
  summarise(score_a = mean(response, na.rm = T)) %>%
  ungroup() %>%
  # group-level mean of means for each mechanism 
  group_by(dev_factor) %>%
  summarise(median = median(score_a, na.rm = T),
            mean = mean(score_a, na.rm = T),
            sd = sd(score_a, na.rm = T)) %>%
  ungroup() %>%
  arrange(dev_factor)

@@

# by domain
d3_mech_ratings_sum_b <- d3_mech_ratings %>%
  # participant-level mean for each mechanism, for each domain
  group_by(ResponseId, dev_factor, factor) %>%
  summarise(score_a = mean(response, na.rm = T)) %>%
  ungroup() %>%
  # group-level mean of means of means for each domain 
  group_by(factor, dev_factor) %>%
  summarise(median = median(score_a, na.rm = T),
            mean = mean(score_a, na.rm = T),
            sd = sd(score_a, na.rm = T)) %>%
  ungroup() %>%
  arrange(factor, dev_factor)

d3_mech_ratings_sum_b %>%
  mutate_if(is.numeric, funs(round_x(., 2)))
```

##### All mechanisms

In brief, this analysis suggested that the perceived importance of these developmental mechanisms varied both overall (see main effects) and across domains (see interaction terms).

```{r s3 mech ratings lmer}
s3_lmer <- lmer(response ~ dev_factor * factor + 
                  (1 | ResponseId) + 
                  (1 | capacity),
                control = lmerControl(optimizer = "bobyqa"),
                data = d3_mech_ratings)

@@

```{r tabs3lmerall, include = T, message = F, warning = F}
model_parameters(s3_lmer, standardize = "refit") %>%
  filter(Effects == "fixed") %>%
  select(Parameter, Coefficient, SE, CI_low, CI_high, t, df_error, p) %>%
  mutate(Parameter = case_when(
    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
    TRUE ~ Parameter)) %>%
  mutate(Parameter = gsub("dev_factorwomb_gm", "Mechanism (Experiences in the womb vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("dev_factorbody_gm", "Mechanism (Body grows and matures vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("dev_factorbrai_gm", "Mechanism (Brain changes vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("dev_factorsens_gm", "Mechanism (Senses improve vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("dev_factorobso_gm", "Mechanism (Observes objects and physical world vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("dev_factorexpt_gm", "Mechanism (Actively experiments vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("dev_factorobsp_gm", "Mechanism (Observes people vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("dev_factorintp_gm", "Mechanism (Interacts with people vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("dev_factorteac_gm", "Mechanism (People explicitly teach vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
  select(-starts_with("CI")) %>%
  select(Parameter, Coefficient, `95% CI`, everything()) %>%
  rename(df = df_error) %>%
  kable("latex", booktabs = T, longtable = T,
        caption = "Study 3, multilevel linear model results (all domains): Fixed effects.",
        digits = 2, align = c("lrrrrrrrrrrrrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

##### Biologically 'preprogrammed'

For the mechanism "the child is biologically 'preprogrammed' to have this ability," this analysis suggested that participants rated this as a particularly important driver of development in the domain of _bodily sensation_, and a relatively unimportant driver of development in the domain of _cognition and control_. See also Figure 3, first row (main text).

```{r s3 mech ratings lmer prep}
s3_lmer_prep <- lmer(response ~ factor +
                       (1 | ResponseId) +
                       (1 | capacity),
                control = lmerControl(optimizer = "bobyqa"),
                data = d3_mech_ratings %>%
                  filter(dev_factor == "preprogrammed"))

summary(s3_lmer_prep)
# model_parameters(s3_lmer_prep)
```

```{r tabs3lmerprep, include = T, message = F, warning = F}
model_parameters(s3_lmer_prep, standardize = "refit") %>%
  filter(Effects == "fixed") %>%
  select(Parameter, Coefficient, SE, CI_low, CI_high, t, df_error, p) %>%
  mutate(Parameter = case_when(
    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
    TRUE ~ Parameter)) %>%
  mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
  select(-starts_with("CI")) %>%
  select(Parameter, Coefficient, `95% CI`, everything()) %>%
  rename(df = df_error) %>%
  kable("latex", booktabs = T, longtable = T,
        caption = "Study 3, multilevel linear model results (biologically 'preprogrammed'): Fixed effects.",
        digits = 2, align = c("lrrrrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

##### Experiences in the womb

For the mechanism "the child has experiences in the womb that give them this ability," this analysis suggested that participants rated this as a particularly important driver of development in the domain of _bodily sensation_, and a relatively unimportant driver of development in the domain of _cognition and control_. See also Figure 3, second row (main text).

```{r s3 mech ratings lmer womb}
s3_lmer_womb <- lmer(response ~ factor +
                       (1 | ResponseId) +
                       (1 | capacity),
                control = lmerControl(optimizer = "bobyqa"),
                data = d3_mech_ratings %>%
                  filter(dev_factor == "womb_experiences"))

summary(s3_lmer_womb)
# model_parameters(s3_lmer_womb)
```

```{r tabs3lmerwomb, include = T, message = F, warning = F}
model_parameters(s3_lmer_womb, standardize = "refit") %>%
  filter(Effects == "fixed") %>%
  select(Parameter, Coefficient, SE, CI_low, CI_high, t, df_error, p) %>%
  mutate(Parameter = case_when(
    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
    TRUE ~ Parameter)) %>%
  mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
  select(-starts_with("CI")) %>%
  select(Parameter, Coefficient, `95% CI`, everything()) %>%
  rename(df = df_error) %>%
  kable("latex", booktabs = T, longtable = T,
        caption = "Study 3, multilevel linear model results (experiences in the womb): Fixed effects.",
        digits = 2, align = c("lrrrrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

##### Body grows and matures

For the mechanism "the child’s body grows and matures (for example, muscles get stronger, child gets taller)," this analysis revealed no significant differences in importance ratings across domains. See also Figure 3, third row (main text).

```{r s3 mech ratings lmer body}
s3_lmer_body <- lmer(response ~ factor +
                       (1 | ResponseId) +
                       (1 | capacity),
                control = lmerControl(optimizer = "bobyqa"),
                data = d3_mech_ratings %>%
                  filter(dev_factor == "body_grows"))

summary(s3_lmer_body)
# model_parameters(s3_lmer_body)
```

```{r tabs3lmerbody, include = T, message = F, warning = F}
model_parameters(s3_lmer_body, standardize = "refit") %>%
  filter(Effects == "fixed") %>%
  select(Parameter, Coefficient, SE, CI_low, CI_high, t, df_error, p) %>%
  mutate(Parameter = case_when(
    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
    TRUE ~ Parameter)) %>%
  mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
  select(-starts_with("CI")) %>%
  select(Parameter, Coefficient, `95% CI`, everything()) %>%
  rename(df = df_error) %>%
  kable("latex", booktabs = T, longtable = T,
        caption = "Study 3, multilevel linear model results (experiences in the womb): Fixed effects.",
        digits = 2, align = c("lrrrrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

##### Brain changes

For the mechanism "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)," this analysis suggested that participants rated this as a particularly important driver of development in the domains of _social connection_ and _cognition and control_. See also Figure 3, fourth row (main text).

```{r s3 mech ratings lmer brai}
s3_lmer_brai <- lmer(response ~ factor +
                       (1 | ResponseId) +
                       (1 | capacity),
                control = lmerControl(optimizer = "bobyqa"),
                data = d3_mech_ratings %>%
                  filter(dev_factor == "brain_changes"))

summary(s3_lmer_brai)
# model_parameters(s3_lmer_brai)
```

```{r tabs3lmerbrai, include = T, message = F, warning = F}
model_parameters(s3_lmer_brai, standardize = "refit") %>%
  filter(Effects == "fixed") %>%
  select(Parameter, Coefficient, SE, CI_low, CI_high, t, df_error, p) %>%
  mutate(Parameter = case_when(
    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
    TRUE ~ Parameter)) %>%
  mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
  select(-starts_with("CI")) %>%
  select(Parameter, Coefficient, `95% CI`, everything()) %>%
  rename(df = df_error) %>%
  kable("latex", booktabs = T, longtable = T,
        caption = "Study 3, multilevel linear model results (experiences in the womb): Fixed effects.",
        digits = 2, align = c("lrrrrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

##### Senses improve

For the mechanism "the child’s senses improve (for example, vision gets sharper, hearing improves)," this analysis revealed no significant differences in importance ratings across domains. See also Figure 3, fifth row (main text).

```{r s3 mech ratings lmer sens}
s3_lmer_sens <- lmer(response ~ factor +
                       (1 | ResponseId) +
                       (1 | capacity),
                control = lmerControl(optimizer = "bobyqa"),
                data = d3_mech_ratings %>%
                  filter(dev_factor == "senses_improve"))

summary(s3_lmer_sens)
# model_parameters(s3_lmer_brai)
```

```{r tabs3lmersens, include = T, message = F, warning = F}
model_parameters(s3_lmer_sens, standardize = "refit") %>%
  filter(Effects == "fixed") %>%
  select(Parameter, Coefficient, SE, CI_low, CI_high, t, df_error, p) %>%
  mutate(Parameter = case_when(
    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
    TRUE ~ Parameter)) %>%
  mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
  select(-starts_with("CI")) %>%
  select(Parameter, Coefficient, `95% CI`, everything()) %>%
  rename(df = df_error) %>%
  kable("latex", booktabs = T, longtable = T,
        caption = "Study 3, multilevel linear model results (experiences in the womb): Fixed effects.",
        digits = 2, align = c("lrrrrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

XXXX BOOKMARK
